ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-12 paper.tex
some fixes and revision to conclusions

\begin{table}
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{p{3cm}p{2cm}p{2cm}}
    \toprule
    Reward condition        & POMDP  & MDP~\cite{lock2019active}   \\ \midrule
    $r(o = o_{target})$     & 10000  & 10000 \\ 
    $r(v = \textrm{true})$  & -75    & -10   \\
    $r(n > n_{\max})$       & -75    & -10   \\
    otherwise $r(\cdot)$    & -100   & -1    \\
    \bottomrule
  \end{tabular}
\end{table}

@@

For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
In this case, the human acts as both the controller and the actuator. 
Similar to other commercially available applications, such as SeeingAI\footnote{apps.apple.com/us/app/seeing-ai/id999062298} and TapTapSee\footnote{play.google.com/store/apps/details?id=com.msearcher.taptapsee.android}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen. 
When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.

@@

The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
Using a dataset specifically designed for active vision tasks that include the absolute positions of objects as well as the camera in a diverse set of real scenes, will make it possible to extend the POMDP model into 3 dimensions and use more accurate transition and observation functions.
The University of North Carolina's Active Vision Dataset\cite{active2017dataset} has a limited set of object and scene classes, but is a step in the right direction.
The usability of the system can potentially be improved by replacing the simple sine-wave tone with a richer and more pleasant tone, such as musical instruments, and allow for the parameters that control the interface's behaviour adapt to the user over time.  
%Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.

@@

\paragraph{{\bf Acknowledgements.}}\label{sec:acknowledge}
This research is partly supported by a Google Faculty Research Award (Winter 2015).
We would like to thank the Voluntary Centre Services UK for their help in facilitating the experiments with people with limited vision. 
%\tofix{any charity directly involved in the experiments?}

>>>>

\begin{table}[t]
  \centering
  \caption{The reward function for the POMDP. }\label{tab:rewards}
  \begin{tabular}{p{3cm}p{2cm}p{2cm}}
    \toprule
    Reward condition        & POMDP  & MDP~\cite{lock2019active}   \\ \midrule
    $r(o = o_{target})$     & 10000  & 10000 \\ 
    $r(v = \textrm{true})$  & -75    & -10   \\
    $r(n > n_{\max})$       & -75    & -10   \\
    otherwise $r(\cdot)$    & -100   & -1    \\
    \bottomrule
  \end{tabular}
\end{table}

@@

For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
In this case, the human acts as both the controller and the actuator. 
Similar to other commercially available applications, such as SeeingAI\footnote{http://www.microsoft.com/en-us/ai/seeing-ai} and TapTapSee\footnote{http://taptapseeapp.com}, the unguided version of our app only reads out the objects upon the user's request by tapping on the screen. 
When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.

@@

The system can benefit from future work that focuses on improving the flexibility and usability of the system. 
New datasets that includes the 3D position of objects and camera, similar to what has been done in robotics~\cite{active2017dataset} but with a more diverse set of real scenes, would make it possible to extend our solution training more accurate transition and observation models that can cope with depth.
The usability of the system can potentially be improved by more sophisticated audio interfaces and creating adaptive control algorithms that change the interface's behaviour based on the user performance over time~\cite{gallina2015}.  
%Furthermore, such a dataset will make it possible to replace the relational transition and observation functions used in this work, with more realistic ones that will allow a wider set of actions to be used.

@@

\paragraph{{\bf Acknowledgements.}}\label{sec:acknowledge}
This research is partly supported by a Google Faculty Research Award.
We would like to thank the Voluntary Centre Services UK for their help in facilitating the experiments with people with limited vision. 
%\tofix{any charity directly involved in the experiments?}
